\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{setspace}
\usepackage{parskip}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\titleformat{\section}{\large\bfseries}{}{0pt}{}[\titlerule]
\titleformat{\subsection}{\bfseries}{}{0pt}{}
\setlist[itemize]{noitemsep,topsep=2pt,leftmargin=1.2em}
\setstretch{1.05}

\newcommand{\role}[1]{\textbf{#1}}

\begin{document}

% ===================== Header =====================
{\LARGE \textbf{Mart\'in Jes\'us Chipoco}}\\[2pt]
Unreal Engine Developer \& Computer Engineer \hfill Vi\~na del Mar, Valpara\'iso, Chile\\
\href{mailto:martinchipoco@gmail.com}{martinchipoco@gmail.com} \,|\,
\href{https://www.linkedin.com/in/mart\%C3\%ADn-jes\%C3\%BAs-chipoco/}{LinkedIn} \,|\,
\href{https://github.com/Noothowl}{GitHub} \

% ===================== Summary =====================
\section*{Professional Summary}
Junior \textbf{Gameplay Engineer \& Software Developer} with expertise in \textbf{Unreal Engine 5} and the \textbf{Gameplay Ability System (GAS)}, and a solid foundation in modern web and cloud technologies.
Experienced in software architecture, engineering workflows, and iterative product development across both game and enterprise contexts.
Skilled at bridging technical and creative domains to build scalable, data-driven systems and tools.

% ===================== Education =====================
\section*{Education}
\textbf{B.Sc. Computer Engineering} (in progress --- expected Dec 2025)\\
Federico Santa Mar\'ia Technical University (UTFSM)\\
Relevant electives: IoT; Mobile Apps; Cloud Computing; Cybersecurity; Optimization Techniques; UI/UX.

\textbf{Project-Based Thesis --- VoD Framework}\\
Design and development of a \textbf{custom modular Unreal Engine 5 build} focused on data-driven workflows and scalability for small studios.
Aims to reduce technical debt in indie pipelines and facilitate \textbf{state-funding readiness} via standardized engineering practices and reusable systems.

% ===================== Technical Skills =====================
\section*{Technical Skills}
\textbf{Core Strengths:} Software Architecture; Iterative Development; Technical Leadership; Product Ownership (PM/PO experience).\\
\textbf{Programming:} C++; JavaScript (Node); Python; Java; C\#; PHP; SQL / NoSQL.\\
\textbf{Engines \& Game Tech:} Unreal Engine 5 (GAS, C++, Blueprints, GameplayTags, Montages); Blender.\\
\textbf{Web / Cloud:} Laravel; Express; React; PostgreSQL; Docker; AWS (Certified).\\
\textbf{Data / Visualization (not primary):} Python (analysis/tooling); Power BI.\\
\textbf{Version Control / DevOps:} Git; GitHub; Git LFS + locking; GitHub Actions.\\
\textbf{Methodologies:} Scrum; PMBOK basics; Agile workflows; Documentation culture.

% ===================== Experience =====================
\section*{Experience}

\subsection*{Gameplay Systems Intern --- Lead Programmer / Product Owner (Tyrant Team) \hfill Aug 2024 -- Nov 2024 (freelance through Dec)}
\begin{itemize}
  \item Architecting and developing a \textbf{custom modular Unreal Engine 5 framework} integrating GAS, data-driven gameplay assets, debug tooling, and universal bone-based hit detection.
  \item Defined project structure, engineering workflow, and CI/CD for an indie-scale development team.
  \item Balanced \textbf{PO / Lead Programmer} responsibilities: backlog definition, iteration scoping, and onboarding documentation.
\end{itemize}
\textit{Stack: UE 5.6, GAS, C++, Blueprints, GameplayTags, Git LFS, iterative prototyping}

\subsection*{Full-Stack Engineer --- Gustavo Fricke Hospital Contactability System \hfill 2024}
\begin{itemize}
  \item Developed a \textbf{contactability system} for patient communication via WhatsApp requiring \textbf{zero} user interaction.
  \item Implemented backend automation (Express + Prisma + PostgreSQL) and a minimal admin dashboard focused on clarity and usability.
  \item Integrated data contracts and validation across layers for reliability in real hospital workflows.
  \item Presented at the \textbf{UTFSM Software Fair 2025} (Equipo Gustabot).
\end{itemize}

\subsection*{Scrum Team Intern --- ELYON Technology \hfill Dec 2022 -- Feb 2023}
\begin{itemize}
  \item Coordinated remote Scrum routines and produced onboarding documentation for experimental enterprise prototypes.
\end{itemize}

\subsection*{Technical Tutor \& Mentor (Freelance) \hfill 2023 -- Present}
\begin{itemize}
  \item Tutored early-stage engineering students in programming, architecture principles, and project planning.
\end{itemize}

\subsection*{Technical Advisor --- Asesor\'ia e Inspecci\'on SPA (part-time) \hfill 2019 -- Present}
\begin{itemize}
  \item IT and automation advisor for a construction company; maintained infrastructure, recommended tools, and assisted with software solutions (webhooks \& apps).
\end{itemize}

% ===================== Leadership & Community =====================
\section*{Leadership \& Community}
\textbf{USM Games --- President / Founder} \hfill Nov 2024 -- Present\\
Leads the university's game-dev initiative; organizes funding, outreach, and guest talks (incl. \textit{Julio Marambio, Octeto Studios}).

\textbf{AEVGC --- Regional Coordinator (Valpara\'iso)} \hfill 2025 -- Present\\
Board member coordinating regional collaboration among universities and indie studios.

% ===================== Projects =====================
\section*{Projects}
\textbf{Litch Rayders --- UE5 Indie Prototype} (2025)\\
Designed and published a solo UE5 prototype demonstrating modular gameplay patterns (Itch.io).

\textbf{Noothowl Vault --- 3D Asset Portfolio} (2022 -- 2023)\\
Created and shared stylized 3D assets for prototyping.

% ===================== Certifications =====================
\section*{Certifications}
AWS Cloud Practitioner (2025); Epic Games Developer Certificate (2025).

% ===================== Interests =====================
\section*{Interests}
Gameplay engineering; Data-driven framework design; Unreal Engine customization; Software architecture; Creative-tech production pipelines.

\end{document}
